---
title: "edouaRd"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a package of practical things I use every day. Thus, it is not really community oriented.

`edouaRd` can be installed from Github :

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("edouardschuppert/edouaRd")
```

# povertext

`povertext` deplete your text, it deletes any accents or umlaut.

```{r}
library(edouaRd, quietly = TRUE)

povertext(c("Père Noël", "Où êtes-vous ?"))

```

# wordfrequency, bigramfrequency & hashtagfrequency

`wordfrequency` splits character strings into words and classifies them, so you know which ones are the most used. `bigramfrequency` does the same thing, but with bigrams. `hashtagfrequency` does the same thing, but with the hashtags. The possibility is offered to keep only part of this data.

```{r}
suppressPackageStartupMessages(library(tidyverse))

edouaRd::rstats %>% 
  wordfrequency(text)

edouaRd::rstats %>% 
  hashtagfrequency(text, slice = 30, original = TRUE)

edouaRd::rstats %>% 
  bigramfrequency(text, slice = 50)
```

# datetimes_fr & dates_fr

`datetimes_fr` turn your datetimes into a french format. `dates_fr` does the same thing, with only the dates. Please note that this is NOT a useful format to work with R. This function can only be used with a purpose of report, in order to have a very understandable format.

```{r}
Sys.time()

datetimes_fr(Sys.time())

dates_fr(Sys.time())

```

# distribution_time

`distribution_time` is used to check the temporal distribution of a dataset.

```{r}
edouaRd::rstats %>% 
  distribution_time(created_at, granularity = "hour")
```

With the `draw` argument, this distribution can be expressed more visually.

```{r}
edouaRd::rstats %>% 
  distribution_time(created_at, granularity = "hour", draw = TRUE)
```

# rm_empty_cols

`rm_empty_cols` allows to delete the columns of an array containing only NAs.

```{r}
edouaRd::rstats

rm_empty_cols(edouaRd::rstats)
```

Please report issues and suggestions to the [issues tracker](https://github.com/edouardschuppert/edouaRd/issues).
